### 2021-08-04 paper/paper.tex
add colliding flows example

  \item Multiple governing equations
  \begin{itemize}
    \item Compressible Euler equations (optionally with self-gravity)
    \item Magnetohydrodynamics equations
    \item Acoustic perturbation equations
    \item Hyperbolic diffusion for elliptic problems
    \item Lattice-Boltzmann equations (D2Q9 and D3Q27 schemes)
    \item Several scalar conservation laws (advection, Burgers)
  \end{itemize}

@@

>>>>

  \item Multiple governing equations
  \begin{itemize}
    \item Compressible Euler equations (optionally with self-gravity)
    \item Magnetohydrodynamics (MHD) equations
    \item Multicomponent compressible Euler and MHD equations
    \item Acoustic perturbation equations
    \item Hyperbolic diffusion for elliptic problems
    \item Lattice-Boltzmann equations (D2Q9 and D3Q27 schemes)
    \item Several scalar conservation laws (advection, Burgers)
  \end{itemize}

@@

Figure~\ref{fig:colliding_flows} demonstrates entropy-dissipative shock-capturing
methods with positivity-preserving limiters and adaptive mesh refinement applied
to supersonic colliding flows inspired by astrophysical setups.

\begin{figure}[htbp]
  \begin{subfigure}{0.53\linewidth}
    \includegraphics[width=\textwidth]{../figures/colliding_flows_density_t15}
    \caption{Density at time $t = 15$.}
  \end{subfigure}%
  \hspace*{\fill}
  \begin{subfigure}{0.47\linewidth}
    \includegraphics[width=\textwidth]{../figures/colliding_flows_mesh_t15}
    \caption{Mesh at time $t = 15$.}
  \end{subfigure}%
  \\
  \begin{subfigure}{0.53\linewidth}
    \includegraphics[width=\textwidth]{../figures/colliding_flows_density_t25}
    \caption{Density at time $t = 25$.}
  \end{subfigure}%
  \hspace*{\fill}
  \begin{subfigure}{0.47\linewidth}
    \includegraphics[width=\textwidth]{../figures/colliding_flows_mesh_t25}
    \caption{Mesh at time $t = 25$.}
  \end{subfigure}%
  \caption{Numerical solutions of two colliding supersonic flows using
           entropy-dissipative shock-capturing methods, positivity-preserving
           limiters, and adaptive mesh refinement for the compressible Euler
           equations.}
  \label{fig:colliding_flows}
\end{figure}
